### 2020-11-02 thesis/thesis.tex
comment 24, umbrella species clarification

This thesis makes use of circuit theory to estimate change to potential functional connectivity for 5 umbrella species, under a certain number of land use change scenarios. These 5 species were selected as their connectivity needs have been shown to be representative of the needs of a larger pool of 14 species (see \cite{albert_applying_2017, meurant_selecting_2018}). See table \ref{tab:species} for a detailed description of the 5 species. Next, we introduce the study region on which we carry these analyses. \\ \vspace{2em}

>>>>

This thesis makes use of circuit theory to estimate change to potential functional connectivity for 5 umbrella species, under a certain number of land use change scenarios. Here we use the term "umbrella species", not in its usual meaning, but to designate species whose connectivity needs have been shown to be representative of the needs of a larger pool of 14 species (see \cite{albert_applying_2017, meurant_selecting_2018}). See table \ref{tab:species} for a detailed description of the 5 species. Next, we introduce the study region on which we carry these analyses. \\ \vspace{2em}
